\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}
\moderncvicons{letters} % FIX: Use letters (T, M, E) instead of icons to avoid missing fontawesome font
\renewcommand{\labelitemi}{\textbullet} % WORKAROUND: Use standard bullet to avoid missing fontawesome font

% adjust the page margins
% adjust the page margins
\usepackage[scale=0.75]{geometry}
\settowidth{\hintscolumnwidth}{08/2023 - 05/2025} % Dynamically measure widest date
\addtolength{\hintscolumnwidth}{1pt} % Add a tiny buffer for safety
\usepackage{lmodern} % FIX: Use scalable fonts to avoid microtype expansion errors

% personal data
\name{}{Bach Chi Le}
\address{Hanoi, Vietnam, 100000}{}{}
\phone[mobile]{+84 798 460 977}
\email{lechibachh@gmail.com}
\homepage{lechibachh.github.io}
\social[linkedin]{lechibachh}

\begin{document}
\makecvtitle

\section{Education}
\cventry{08/2023 - 05/2025}{Master of Science in Financial Engineering}{}{}{}{
\textit{Lehigh University}
\newline
Grade: 3.93/4.0}
\cventry{08/2020 - 07/2023}{Bachelor of Commerce in Finance and Economics}{}{}{}{
\textit{University of Melbourne}
\newline
Grade: First Class Honours (H1)}



\section{Awards and Honors}
\cvitem{2024}{Graduate Business Life Leadership Award, Lehigh University}
\cvitem{2024}{Center for Financial Services Research Fellowship, Lehigh University}
\cvitem{2023}{Director’s Scholarship, Lehigh University}
\cvitem{2022}{Melbourne International Undergraduate Scholarship, University of Melbourne}
\cvitem{2020}{Bachelor of Commerce Global Scholarship, University of Melbourne}

\section{Publications}
\subsection{Preprints}
\cvitem{2025}{\textbf{Tight Robustness Certificates and Wasserstein Distributional Attacks for Deep Neural Networks}
\newline \textbf{Le, B. C.}, Dao, T. V., Nguyen, B. T., \& Chu, H. T. M.
\newline \textit{\href{https://arxiv.org/abs/2510.10000}{arXiv preprint arXiv:2510.10000}.}}





\subsection{Presentations}
\cvitem{01/2025}{\textbf{Mixed versus Traditional Multiple Team Membership Configurations: Understanding Team Satisfaction through the Mediating Role of Identity and Moderating Effect of Intra-Team Conflict}
\newline Moore, O. A., Mchiri, A., Grady-Moreno, A., \& \textbf{Le, B. C.}
\newline \textit{Presented at the \href{https://s3.amazonaws.com/ClubExpressClubFiles/300815/documents/2025_INGRoup_Midyear_Conference_Program_Full_MS-2025v3_2146650323.pdf?AWSAccessKeyId=AKIA6MYUE6DNNJ6ROIH3\&Expires=1767970510\&response-content-disposition=inline\%3B\%20filename\%3D2025_INGRoup_Midyear_Conference_Program_Full_MS-2025v3.pdf\&Signature=RoiZfmZN4oZ06ByM5IWRPPZkJHQ\%3D}{INGRoup 2025 Midyear Conference}, Virtual.}}

\section{Research Experience}
\subsection{\textit{VinUniversity}}
\cventry{06/2025 - Present}{Mathematical Analysis of Modern Deep Learning Architectures}{}{}{}{
\textit{Advisors: Prof. Binh T. Nguyen \& Prof. Hong T. M. Chu}
\newline
Investigating the stability and convergence of deep learning dynamics using tools from optimal transport, mean-field theory, and Lipschitz analysis.}

\subsection{\textit{Lehigh University}}
\cventry{09/2024 - 05/2025}{Adaptive Distributionally Robust Optimization for Time Series}{}{}{}{
\textit{Advisor: Prof. Lam M. Nguyen}
\newline
Derived a tractable convex reformulation of the Adaptive Distributionally Robust Optimization problem for ensemble time series forecasting, analyzed its computational complexity, and validated its predictive performance.}

\cventry{04/2024 - 05/2025}{Risk Management in Deregulated Markets}{}{}{}{
\textit{Advisor: Prof. Alberto J. Lamadrid}
\newline
Benchmarked risk management strategies in deregulated commodity markets, analyzed theorectical bounds, and derived equivalence conditions between Stochastic, Robust, and Info-Gap Optimization frameworks.}

\cventry{01/2024 - 05/2025}{Optimal Structure of Pemantle’s Min-Plus Binary Trees}{}{}{}{
\textit{Advisor: Prof. Si Tang}
\newline
Studied the conjecture that balanced Pemantle’s Min-Plus binary trees yield the maximal expected root value via probabilistic induction and computational verification.}

\cventry{11/2023 - 05/2025}{Statistical Analysis of Multiple Team Membership Dynamics}{}{}{}{
\textit{Advisor: Prof. Ozias A. Moore}
\newline
Analyzed the effects of multiple team membership configurations using multi-level modeling and Monte Carlo simulation techniques to assess mediation pathways and organizational outcomes.}

\subsection{\textit{University of Melbourne}}
\cventry{09/2022 - 11/2022}{The Short Interest Effect in Stocks}{}{}{}{
\textit{Advisors: Prof. Nitin Yadav \& Prof. Peter L. Bossaerts}
\newline
Investigated the empirical persistence of the short interest anomaly in US equities by designing algorithmic strategies to isolate behavioral inefficiencies using momentum signals and mean-variance optimization.}

\section{Teaching Experience}
\cventry{02/2026 - 06/2026}{MATH4010: Advanced Probability and Statistics}{}{}{}{
\textit{VinUniversity}
\newline
Teaching Assistant}

\section{Professional Experience}
\cventry{06/2024 - 08/2024}{Complex Securities \& Financial Instruments Intern}{}{}{}{
\textit{Stout Risius Ross, New York, NY}
\newline
Developed Monte Carlo simulations \& pricing models for complex, illiquid instruments.}

\cventry{05/2024 - 04/2025}{Mathematics Consultant}{}{}{}{
\textit{Outlier AI, San Francisco, CA}
\newline
Evaluated and refined mathematical reasoning in Large Language Models.}

\cventry{04/2023 - 04/2024}{Research Consultant}{}{}{}{
\textit{WorldQuant, Hanoi, Vietnam}
\newline
Developed and backtested quantitative alpha strategies for global equity markets.}



\end{document}
